\LARGE\textbf{Designing Studies and Evaluating Research Results:\\ Type M and Type S Errors for\\ Pearson Correlation Coefficient }

### 2020-05-06 Documents/Paper_main/Paper_main.Rnw
Corrige Altoè

\title{\LARGE\textbf{Designing Studies and Evaluating Research Results:\\
Type M and Type S Errors for Pearson Correlation Coefficient
}}

@@

<<Plot_rho,warning=F, fig.pos="!h", fig.align="center", fig.height=3, fig.width=6, fig.cap="The behaviour of Type M and Type S errors as a function of statistical power in the case of Peardson's correlation $\\rho$." >>=
load("../../data/data_conditions_rho.rda")

>>>>

\title{\LARGE\textbf{Designing Studies and Evaluating Research Results:\\
Type M and Type S Errors for\\ Pearson Correlation Coefficient
}}

@@

<<Plot_rho,warning=F, fig.pos="!h", fig.align="center", fig.height=3, fig.width=6, fig.cap="The behaviour of Type M and Type S errors as a function of statistical power in the case of Pearson's correlation $\\rho$." >>=
load("../../data/data_conditions_rho.rda")
